The value of early warning systems for pandemic response

### 2024-03-02 archive/reproduce-results.qmd
running styler

```{r}
# The r object contains the results objects used in this file
if(!file.exists("./output/r.rds")) {
  source("./R/scripts/run_analysis.R")
} else {
  source("./R/library.R")
  r <- readRDS("./output/r.rds")
}

```

>>>>

```{r}
# The r object contains the results objects used in this file
if (!file.exists("./output/r.rds")) {
  source("./R/scripts/run_analysis.R")
} else {
  source("./R/library.R")
  r <- readRDS("./output/r.rds")
}
```
